\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-18 paper.qmd
Add sample view and select the positions
Update decide fit

<!--langevitour with pD model for S-curve-->
::: {#fig-scurve-sc layout-ncol="3" fig-pos="H"}
![](figures/scurve/sc_1.png)

@@

The appropriate model for the S-curve using UMAP (n_neighbors: $15$) was created with $420$ bins. It was determined to be the best model after removing edges with a length greater than $0.134$. The decision was made considering that the model accurately captures the geometry of the S-curve by fitting the points everywhere (@fig-scurve_sc_best).

In contrast, a poor model for the S-curve with UMAP was created using only $190$ bins and removing edges with a length greater than $0.3$. This model is inadequate as it has a higher MSE compared to the appropriate model. Visually, the model does not fit the points in some places and mismatches the pattern (@fig-scurve-sc-bad).

>>>>

<!--langevitour with pD model for S-curve-->
::: {#fig-scurve-sc layout-ncol="4" fig-pos="H"}
![](figures/scurve/umap_view_copy.png)

![](figures/scurve/sc_1.png)

@@

The appropriate model for the S-curve using UMAP (n_neighbors: $15$) was created with $420$ bins. It was determined to be the best model after removing edges with a length greater than $0.134$. The decision was made considering that the model accurately captures the geometry of the S-curve. But better in some places only (@fig-scurve_sc_best).

In contrast, a poor model for the S-curve with PHATE was created using only $190$ bins and removing edges with a length greater than $0.3$. This model is inadequate as it has a higher MSE compared to the appropriate model. Visually, the model squeezed to the middle of the geometry of the S-curve (@fig-scurve-sc-bad).

### 2024-06-18 paper.tex
Add sample view and select the positions
Update decide fit

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_1.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_2.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_3.png}\end{minipage}%

@@

The appropriate model for the S-curve using UMAP (n\_neighbors: \(15\))
was created with \(420\) bins. It was determined to be the best model
after removing edges with a length greater than \(0.134\). The decision
was made considering that the model accurately captures the geometry of
the S-curve by fitting the points everywhere
(\textbf{?@fig-scurve\_sc\_best}).

In contrast, a poor model for the S-curve with UMAP was created using
only \(190\) bins and removing edges with a length greater than \(0.3\).
This model is inadequate as it has a higher MSE compared to the
appropriate model. Visually, the model does not fit the points in some
places and mismatches the pattern (\textbf{?@fig-scurve-sc-bad}).

>>>>

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/umap_view_copy.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_1.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_2.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_3.png}\end{minipage}%

@@

The appropriate model for the S-curve using UMAP (n\_neighbors: \(15\))
was created with \(420\) bins. It was determined to be the best model
after removing edges with a length greater than \(0.134\). The decision
was made considering that the model accurately captures the geometry of
the S-curve. But better in some places only
(\textbf{?@fig-scurve\_sc\_best}).

In contrast, a poor model for the S-curve with PHATE was created using
only \(190\) bins and removing edges with a length greater than \(0.3\).
This model is inadequate as it has a higher MSE compared to the
appropriate model. Visually, the model squeezed to the middle of the
geometry of the S-curve (\textbf{?@fig-scurve-sc-bad}).
